What do incoming university students believe about open science practices in

### 2021-05-11 analysis/Manuscript.Rmd
create table for norms in practice

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  mutate(Practice = practice) %>% 
  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices. These practices corresponded approximately to the ten norm-counternorm pairs, albeit with one norm excluded on the basis of not referring to behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request). For many of these practices, participants estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants seemed to perceived that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers. It is perhaps fair to say that participants mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.

>>>>

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  rename(Practice = practice) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices. These practices corresponded approximately to the ten norm-counternorm pairs, albeit with one norm excluded on the basis of not referring to behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request). For many of these practices, participants estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants seemed to perceive that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers. It is perhaps fair to say that participants' mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.

```{r norms in practice}

# select columns that relate to norms in practice & pivot it long & drop the na values
in_prac_long <- df %>% 
  dplyr::select(c(id,preregistration:open_access)) %>% 
      pivot_longer (cols = -id,
                names_to = "practice",
                values_to = "prevalence rating") %>% 
  drop_na()

# get the n values for each of the practices
in_prac_counts <- in_prac_long %>% 
  dplyr::group_by(practice) %>% 
  count() %>% 
  ungroup()

# calculate means
in_prac_ms_sds <- in_prac_long %>%
  dplyr::group_by(practice) %>%
  summarise(mean = mean(`prevalence rating`),
            sd = sd(`prevalence rating`)) %>%
  ungroup()

# join the n values with the means
in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)

# calculate 95% CIs
error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
in_prac_means$lower <- in_prac_means$mean - error
in_prac_means$upper <- in_prac_means$mean + error

# combine means & SDs
in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
                          " (", 
                          round_tidy(in_prac_means$sd,2),
                            ")", 
                            " [",
                            round_tidy(in_prac_means$lower,2),
                            ", ", 
                            round_tidy(in_prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
in_practice_means <- in_prac_means %>% 
  dplyr::select(practice, `Prevalence Ratings`) %>% 
  rename(Practice = practice)

# breadcrumbs:
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers

knitr::kable(in_practice_means,
             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
             digits = 2,
             align = c('lc'))
